Accessing the COVID-19 Death Rate in the US: While It Varies Across Different Income Levels, the Impact of Political Preference is Unignorable

### 2023-11-01 outputs/paper/paper.qmd
Update the title and abstract

---
title: "aaaa"
title-block-banner: true
author: "Yiliu Cao"
thanks: "Code and data from this analysis are available at: https://github.com/yiliuc/COVID_US_county.git"
date: "today"
date-format: "long"
abstract: "sssss"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Accessing the COVID-19 Death Rate in the US: While It Varies Across Different Income Levels, the Impact of Political Preference is Unignorable"
title-block-banner: true
author: "Yiliu Cao"
thanks: "Code and data from this analysis are available at: https://github.com/yiliuc/COVID_US_county.git"
date: "today"
date-format: "long"
abstract: "This study utilizes the data on socio-economic factors, COVID-19 statistics, and election results sourced from the American Community Survey, the Center for Systems Science and Engineering (CSSE) at Johns Hopkins University, and Fox News. Primary findings indicate that the death rate increases as the voting for the Republican party rises, and the wealthier the county, the less the death number. While the Democratic Party favors the more affluent counties, the potential reason behind this is that people living in wealthier counties are more educated. Moreover, the prevalence of private insurance in these counties could be another factor contributing to fewer deaths. Future research should focus on more correlated variables, such as hospital capacity."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
